---
output:
  pdf_document:
    includes:
      in_header: gw_forecast_report.tex
    latex_engine: xelatex
params:
  well_id: NULL
  well_location: NULL
  well_tag_number: NULL
  aquifer_num: NULL
  aquifer_type: NULL
  model_type: NULL
  plot: NULL
  table: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(gt)
```

\vspace*{-1.75cm}

\begin{center}
\section*{Observation Well: `r paste0(params$well_id, " - ", params$well_location)`}
\vspace{-2.2em}
\end{center}

\begin{center}
\textbf{`r params$aquifer_num` | `r params$aquifer_type`}
\vspace{-1.5em}
\end{center}

\begin{center}
\textbf{`r params$model_type` | Forecast Issued: `r Sys.Date()`}
\vspace{-1.5em}
\end{center}

```{r plot, fig.height=6, fig.width=10}
params$plot
```


\begin{center}
\section*{Likelihood of Groundwater Level Conditions (\%)}
\vspace{-2.5em}
\end{center}

```{r table}
params$table %>% 
  # as_latex() %>% 
  tab_options(latex.use_longtable=TRUE,
              table.font.size = px(15))#%>%
# opt_table_format(format = "latex")

#   
#   
# tb <- params$table %>%
#   mutate(across(
#     .cols = -1,  # Skip the first column
#     .fns = ~ as.numeric(gsub("[^0-9.]", "", .x)),  # Strip <, >, and convert
#     .names = "{.col}"
#   ))# %>% 
#  # select(c(1,6:9))
# 
# tb <- tb %>% 
#   gt() %>% 
#   # as_latex() %>% 
#   tab_options(latex.use_longtable=TRUE) %>%
#   tab_style(
#     style = cell_fill(color = "lightgreen"),
#     locations = cells_body(
#       columns = 2:5,  # Columns 2 to 5 (time periods)
#       rows = tb[[2]] >= 95 |
#         tb[[3]] >= 95 |
#         tb[[4]] >= 95 |
#         tb[[5]] >= 95
#     )
#   )
# # tb <- as.character(tb)
# # 
# # latex_code_clean <- gsub("\\\\begin\\{table\\}\\[.*\\]", "", tb)
# # latex_code_clean <- gsub("\\\\end\\{table\\}", "", latex_code_clean)
# # 
# # 
# # cat(latex_code_clean)
# tb
# # params$table %>%
#   knitr::kable(
#     format = "latex",
#     align = "l",
#    # booktabs = TRUE,
#    # longtable = TRUE,
#     linesep = "") %>%
#   kableExtra::kable_styling(
#       # position = "left",
#       latex_options = c("striped", "hold_position")
#       # stripe_color = "gray!15"
#     )
```

**Disclaimer**: Groundwater level forecasts use statistical models and third-party data. These models have two types of errors: systematic (model limitations) and random (input data). Forecasts may differ from actual observations, and water levels could exceed forecast bounds. Users must accept responsibility for their use and interpretation.

\begin{center}
Model Information: \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{Detailed explanation of chart}} | \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{Technical reference for model}} | \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{Forecast Map}}\\

Well Information: \textcolor{blue}{\href{`r paste0("https://aqrt.nrs.gov.bc.ca/Data/Location/Summary/Location/",params$well_id,"/Interval/Latest")`}{BC Real-time Data}} | \textcolor{blue}{\href{`r paste0("https://apps.nrs.gov.bc.ca/gwells/well/", params$well_tag_number)`}{Well Summary}} | \textcolor{blue}{\href{`r paste0("https://apps.nrs.gov.bc.ca/gwells/aquifers/",params$aquifer_num)`}{Aquifer Summary}}


Issued by \textcolor{blue}{\href{https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/drought-flooding-dikes-dams/river-forecast-centre}{BC River Forecast Centre}} | Updated: `r format(Sys.time(), "%Y-%m-%d %H:%M")`

\end{center}

